Long_time_series

### 2019-04-02 Detect_MCSs.Rmd
updated

This script is very repetitive. Wavelet.Rmd creates a function to do this.

@@

combined_US <- rbind(UC_1,UC_2)
#save(combined_US, file = "Data/combined_US.RData")
SACTN_temps_US <- SACTN_daily_v4.2 %>%
  left_join(site_list[,c(4,13)], by = "index") %>%
  filter(index %in% combined_US$index)

@@

Here I write a function to match the remotely-sensed SST to the *in-situ* collected SST

@@

#SACTN
```{r}
ts <- ts2clm(SACTN_PN, climatologyPeriod = c("1974-01-01", "2016-12-31"),
             pctile = 10)
res <- detect_event(ts, coldSpells = TRUE)
MCS <- res$climatology # Show a portion of the climatology
MCS_events <- res$event[1:5,1:10] # Show some of the cold-spells
# MCS <- MCS[14408:15503,] # Get the years from 2013 - 2015

MCS_SACTN_PN <- event_line(res, spread = 100, metric = "intensity_cumulative",
           start_date = "1974-01-01", end_date = "1977-12-31")

@@

ts <- ts2clm(MUR_SST_PN, climatologyPeriod = c("2002-06-01", "2015-12-30"), pctile = 10)
res <- detect_event(ts, coldSpells = TRUE)
MCS <- res$climatology
MCS_MUR_PN <- event_line(res, spread = 500, metric = "intensity_cumulative",
           start_date = "2011-12-31", end_date = "2014-10-30") +
  ggtitle("MUR_PN") +
  theme(legend = "Bottom")

@@

MUR_SST_DI <- MUR_SST %>%
  filter(site == "Dassen Island") %>% 
  dplyr::rename(temp = nearest1) %>% 
  select(date, temp) %>% 
  dplyr::rename(t = date)

ts <- ts2clm(MUR_SST_DI, climatologyPeriod = c("2002-06-01", "2015-12-30"), pctile = 10)
res <- detect_event(ts, coldSpells = TRUE)
MCS <- res$climatology
MCS_MUR_DI <- event_line(res, spread = 500, metric = "intensity_cumulative",
           start_date = "2011-12-31", end_date = "2014-10-30") +
  ggtitle("MUR_DI")

MUR_SST_HB <- MUR_SST %>%
  filter(site == "Hout Bay") %>% 
  dplyr::rename(temp = nearest1) %>% 
  select(date, temp) %>% 
  dplyr::rename(t = date)

ts <- ts2clm(MUR_SST_HB, climatologyPeriod = c("2002-06-01", "2015-12-30"), pctile = 10)
res <- detect_event(ts, coldSpells = TRUE)
MCS <- res$climatology
MCS_MUR_HB <- event_line(res, spread = 500, metric = "intensity_cumulative",
           start_date = "2011-12-31", end_date = "2014-10-30") +
  ggtitle("MUR_HB")

@@

combined_MUR <- ggarrange(MCS_MUR_PN, MCS_MUR_LB, MCS_MUR_O, MCS_MUR_HB, MCS_MUR_SP, MCS_MUR_Kom, MCS_MUR_DI, MCS_MUR_SB, MCS_MUR_YZ, ncol = 3, nrow = 3)
```

# G1SST
```{r}
load("Data/G1SSTsub_SST.RData")

@@

ts <- ts2clm(G1SSTsub_SST_PN, climatologyPeriod = c("1991-09-01", "2015-12-30"), pctile = 10)
res <- detect_event(ts, coldSpells = TRUE)
MCS <- res$climatology
MCS_g1sst_PN <- event_line(res, spread = 500, metric = "intensity_cumulative",
           start_date = "1991-09-01", end_date = "1992-12-30") +
  ggtitle("G1SST_PN")

@@

ts <- ts2clm(G1SSTsub_SST_LB, climatologyPeriod = c("1991-09-01", "2015-12-30"), pctile = 10)
res <- detect_event(ts, coldSpells = TRUE)
MCS <- res$climatology
MCS_g1sst_LB <- event_line(res, spread = 500, metric = "intensity_cumulative",
           start_date = "1991-09-01", end_date = "1992-12-30") +
  ggtitle("G1SST_LB")

@@

ts <- ts2clm(G1SSTsub_SST_SB, climatologyPeriod = c("1991-09-01", "2015-12-30"), pctile = 10)
res <- detect_event(ts, coldSpells = TRUE)
MCS <- res$climatology
MCS_g1sst_SB <- event_line(res, spread = 500, metric = "intensity_cumulative",
           start_date = "1991-09-01", end_date = "1992-12-30") +
  ggtitle("G1SST_SB")

@@

ts <- ts2clm(G1SSTsub_SST_YZ, climatologyPeriod = c("1991-09-01", "2015-12-30"), pctile = 10)
res <- detect_event(ts, coldSpells = TRUE)
MCS <- res$climatology
MCS_g1sst_YZ <- event_line(res, spread = 500, metric = "intensity_cumulative",
           start_date = "1991-09-01", end_date = "1992-12-30") +
  ggtitle("G1SST_YZ")

G1SSTsub_SST_HB <- G1SSTsub_SST %>% 
  filter(site == "Hout Bay") %>% 
  dplyr::rename(temp = nearest1) %>% 
  select(date, temp) %>% 
  dplyr::rename(t = date)

ts <- ts2clm(G1SSTsub_SST_HB, climatologyPeriod = c("1991-09-01", "2015-12-30"), pctile = 10)
res <- detect_event(ts, coldSpells = TRUE)
MCS <- res$climatology
MCS_g1sst_HB <- event_line(res, spread = 500, metric = "intensity_cumulative",
           start_date = "1991-09-01", end_date = "1992-12-30") +
  ggtitle("G1SST_HB")

@@

ts <- ts2clm(G1SSTsub_SST_SP, climatologyPeriod = c("1991-09-01", "2015-12-30"), pctile = 10)
res <- detect_event(ts, coldSpells = TRUE)
MCS <- res$climatology
MCS_g1sst_SP <- event_line(res, spread = 500, metric = "intensity_cumulative",
           start_date = "1991-09-01", end_date = "1992-12-30") +
  ggtitle("G1SST_SP")

@@

ts <- ts2clm(G1SSTsub_SST_O, climatologyPeriod = c("1991-09-01", "2015-12-30"), pctile = 10)
res <- detect_event(ts, coldSpells = TRUE)
MCS <- res$climatology
MCS_g1sst_O <- event_line(res, spread = 500, metric = "intensity_cumulative",
           start_date = "1991-09-01", end_date = "1992-12-30") +
  ggtitle("G1SST_O")

@@

ts <- ts2clm(G1SSTsub_SST_Kom, climatologyPeriod = c("1991-09-01", "2015-12-30"), pctile = 10)
res <- detect_event(ts, coldSpells = TRUE)
MCS <- res$climatology
MCS_g1sst_Kom <- event_line(res, spread = 500, metric = "intensity_cumulative",
           start_date = "1991-09-01", end_date = "1992-12-30") +
  ggtitle("G1SST_Kom")

G1SSTsub_SST_DI <- G1SSTsub_SST %>% 
  filter(site == "Dassen Island") %>% 
  dplyr::rename(temp = nearest1) %>% 
  select(date, temp) %>% 
  dplyr::rename(t = date)

ts <- ts2clm(G1SSTsub_SST_DI, climatologyPeriod = c("1991-09-01", "2015-12-30"), pctile = 10)
res <- detect_event(ts, coldSpells = TRUE)
MCS <- res$climatology
MCS_g1sst_DI <- event_line(res, spread = 500, metric = "intensity_cumulative",
           start_date = "1991-09-01", end_date = "1992-12-30") +
  ggtitle("G1SST_DI")

@@

ts <- ts2clm(G1SSTsub_SST_SB, climatologyPeriod = c("1991-09-01", "2015-12-30"), pctile = 10)
res <- detect_event(ts, coldSpells = TRUE)
MCS <- res$climatology
MCS_g1sst_SB <- event_line(res, spread = 500, metric = "intensity_cumulative",
           start_date = "1991-09-01", end_date = "1992-12-30") +
  ggtitle("G1SST_SB")

G1SSTsub_SST_HB <- G1SSTsub_SST %>% 
  filter(site == "Hout Bay") %>% 
  dplyr::rename(temp = nearest1) %>% 
  select(date, temp) %>% 
  dplyr::rename(t = date)

ts <- ts2clm(G1SSTsub_SST_HB, climatologyPeriod = c("1991-09-01", "2015-12-30"), pctile = 10)
res <- detect_event(ts, coldSpells = TRUE)
MCS <- res$climatology
MCS_g1sst_HB <- event_line(res, spread = 500, metric = "intensity_cumulative",
           start_date = "1991-09-01", end_date = "1992-12-30") +
  ggtitle("G1SST_HB")

combined_G1SST <- ggarrange(MCS_g1sst_PN, MCS_g1sst_LB, MCS_g1sst_O, MCS_g1sst_SP, MCS_g1sst_Kom, MCS_g1sst_DI, MCS_g1sst_YZ, MCS_g1sst_SB, MCS_g1sst_HB, ncol = 3, nrow = 3)
```

@@

ts <- ts2clm(OISST_PN, climatologyPeriod = c("1981-09-01", "2018-06-30"), pctile = 10)
res <- detect_event(ts, coldSpells = TRUE)
MCS <- res$climatology
MCS_OISST_PN <- event_line(res, spread = 500, metric = "intensity_cumulative",
           start_date = "2016-09-01", end_date = "2018-06-30") +
  ggtitle("OISST_PN")

@@

ts <- ts2clm(OISST_LB, climatologyPeriod = c("1981-09-01", "2018-06-30"), pctile = 10)
res <- detect_event(ts, coldSpells = TRUE)
MCS <- res$climatology
MCS_OISST_LB <- event_line(res, spread = 500, metric = "intensity_cumulative",
           start_date = "2016-09-01", end_date = "2018-06-30") +
  ggtitle("OISST_LB")

@@

ts <- ts2clm(OISST_SB, climatologyPeriod = c("1981-09-01", "2018-06-30"), pctile = 10)
res <- detect_event(ts, coldSpells = TRUE)
MCS <- res$climatology
MCS_OISST_SB <- event_line(res, spread = 500, metric = "intensity_cumulative",
           start_date = "2016-09-01", end_date = "2018-06-30") +
  ggtitle("OISST_SB")

@@

ts <- ts2clm(OISST_YZ, climatologyPeriod = c("1981-09-01", "2018-06-30"), pctile = 10)
res <- detect_event(ts, coldSpells = TRUE)
MCS <- res$climatology
MCS_OISST_YZ <- event_line(res, spread = 500, metric = "intensity_cumulative",
           start_date = "2016-09-01", end_date = "2018-06-30") +
  ggtitle("OISST_YZ")

OISST_DI <- OISST_sites %>% 
  filter(site == "Dassen Island") %>% 
  select(date, temp) %>% 
  dplyr::rename(t = date)

ts <- ts2clm(OISST_DI, climatologyPeriod = c("1981-09-01", "2018-06-30"), pctile = 10)
res <- detect_event(ts, coldSpells = TRUE)
MCS <- res$climatology
MCS_OISST_DI <- event_line(res, spread = 500, metric = "intensity_cumulative",
           start_date = "2016-09-01", end_date = "2018-06-30") +
  ggtitle("OISST_DI")

@@

ts <- ts2clm(OISST_SP, climatologyPeriod = c("1981-09-01", "2018-06-30"), pctile = 10)
res <- detect_event(ts, coldSpells = TRUE)
MCS <- res$climatology
MCS_OISST_SP <- event_line(res, spread = 500, metric = "intensity_cumulative",
           start_date = "2016-09-01", end_date = "2018-06-30") +
  ggtitle("OISST_SP")

@@

ts <- ts2clm(OISST_Kom, climatologyPeriod = c("1981-09-01", "2018-06-30"), pctile = 10)
res <- detect_event(ts, coldSpells = TRUE)
MCS <- res$climatology
MCS_OISST_Kom <- event_line(res, spread = 500, metric = "intensity_cumulative",
           start_date = "2016-09-01", end_date = "2018-06-30") +
  ggtitle("OISST_Kom")

@@

ts <- ts2clm(OISST_O, climatologyPeriod = c("1981-09-01", "2018-06-30"), pctile = 10)
res <- detect_event(ts, coldSpells = TRUE)
MCS <- res$climatology
MCS_OISST_O <- event_line(res, spread = 500, metric = "intensity_cumulative",
           start_date = "2016-09-01", end_date = "2018-06-30") +
  ggtitle("OISST_O")

OISST_HB <- OISST_sites %>% 
  filter(site == "Hout Bay") %>% 
  select(date, temp) %>% 
  dplyr::rename(t = date)

ts <- ts2clm(OISST_HB, climatologyPeriod = c("1981-09-01", "2018-06-30"), pctile = 10)
res <- detect_event(ts, coldSpells = TRUE)
MCS <- res$climatology
MCS_OISST_HB <- event_line(res, spread = 500, metric = "intensity_cumulative",
           start_date = "2016-09-01", end_date = "2018-06-30") +
  ggtitle("OISST_HB")

combined_OISST <- ggarrange(MCS_OISST_PN, MCS_OISST_LB, MCS_OISST_SB, MCS_OISST_YZ, MCS_OISST_O, MCS_OISST_HB, MCS_OISST_Kom,MCS_OISST_SP, MCS_OISST_DI)
```

# K10
Time series is less than 10 years and so the detection of MCS is not effective. 
heatwaveR package may be applied to datasets that have a climatological period of >10years

>>>>

** This script is very repetitive. Wavelet.Rmd creates a function to do this **

@@

# combined_US <- rbind(UC_1,UC_2)
#save(combined_US, file = "Data/combined_US.RData")
SACTN_temps_US <- SACTN_daily_v4.2 %>%
  left_join(site_list[,c(4,13)], by = "index") %>%
  filter(index %in% combined_US$index)

@@

This function matches the remotely-sensed SST to the *in-situ* collected SST

@@

#SACTN.....
```{r}
ts <- ts2clm(SACTN_PN, climatologyPeriod = c("1974-01-01", "2016-12-31"),
             pctile = 10)
res <- detect_event(ts, coldSpells = TRUE)
MCS <- res$climatology # Show a portion of the climatology
MCS_events <- res$event[1:5,1:10] # Show some of the cold-spells
# MCS <- MCS[14408:15503,] # Get the years from 2013 - 2015

MCS_SACTN_PN <- event_line(res, spread = 500, metric = "intensity_cumulative",
           start_date = "1974-01-01", end_date = "2015-12-31")

@@

ts <- ts2clm(MUR_SST_PN, climatologyPeriod = c("2002-06-01", "2015-12-30"), pctile = 10)
res <- detect_event(ts, coldSpells = TRUE)
MCS <- res$climatology
MCS_MUR_PN <- event_line(res, spread = 500, metric = "intensity_cumulative",
           start_date = "2011-12-31", end_date = "2014-10-30") +
  ggtitle("MUR_PN")

@@

@@

combined_MUR <- ggarrange(MCS_MUR_PN, MCS_MUR_LB, MCS_MUR_O, MCS_MUR_SP, MCS_MUR_KoM, MCS_MUR_SB, MCS_MUR_YZ, ncol = 2, nrow = 4)
```

# G1SST

```{r}
load("Data/G1SSTsub_SST.RData")

@@

ts <- ts2clm(G1SSTsub_SST_PN, climatologyPeriod = c("1991-09-01", "2015-12-30"), pctile = 10)
res <- detect_event(ts, coldSpells = TRUE)
MCS <- res$climatology
MCS_g1sst_PN <- event_line(res, spread = 500, metric = "intensity_cumulative",
           start_date = "2011-12-31", end_date = "2014-10-30") +
  ggtitle("G1SST_PN")

@@

ts <- ts2clm(G1SSTsub_SST_LB, climatologyPeriod = c("1991-09-01", "2015-12-30"), pctile = 10)
res <- detect_event(ts, coldSpells = TRUE)
MCS <- res$climatology
MCS_g1sst_LB <- event_line(res, spread = 500, metric = "intensity_cumulative",
           start_date = "2011-12-31", end_date = "2014-10-30") +
  ggtitle("G1SST_LB")

@@

ts <- ts2clm(G1SSTsub_SST_SB, climatologyPeriod = c("1991-09-01", "2015-12-30"), pctile = 10)
res <- detect_event(ts, coldSpells = TRUE)
MCS <- res$climatology
MCS_g1sst_SB <- event_line(res, spread = 500, metric = "intensity_cumulative",
           start_date = "2011-12-31", end_date = "2014-10-30") +
  ggtitle("G1SST_SB")

@@

ts <- ts2clm(G1SSTsub_SST_YZ, climatologyPeriod = c("1991-09-01", "2015-12-30"), pctile = 10)
res <- detect_event(ts, coldSpells = TRUE)
MCS <- res$climatology
MCS_g1sst_YZ <- event_line(res, spread = 500, metric = "intensity_cumulative",
           start_date = "2011-12-31", end_date = "2014-10-30") +
  ggtitle("G1SST_YZ")

@@

ts <- ts2clm(G1SSTsub_SST_SP, climatologyPeriod = c("1991-09-01", "2015-12-30"), pctile = 10)
res <- detect_event(ts, coldSpells = TRUE)
MCS <- res$climatology
MCS_g1sst_SP <- event_line(res, spread = 500, metric = "intensity_cumulative",
           start_date = "2011-12-31", end_date = "2014-10-30") +
  ggtitle("G1SST_SP")

@@

ts <- ts2clm(G1SSTsub_SST_O, climatologyPeriod = c("1991-09-01", "2015-12-30"), pctile = 10)
res <- detect_event(ts, coldSpells = TRUE)
MCS <- res$climatology
MCS_g1sst_O <- event_line(res, spread = 500, metric = "intensity_cumulative",
           start_date = "2011-12-31", end_date = "2014-10-30") +
  ggtitle("G1SST_O")

@@

ts <- ts2clm(G1SSTsub_SST_Kom, climatologyPeriod = c("1991-09-01", "2015-12-30"), pctile = 10)
res <- detect_event(ts, coldSpells = TRUE)
MCS <- res$climatology
MCS_g1sst_Kom <- event_line(res, spread = 500, metric = "intensity_cumulative",
           start_date = "2011-12-31", end_date = "2014-10-30") +
  ggtitle("G1SST_Kom")

@@

ts <- ts2clm(G1SSTsub_SST_SB, climatologyPeriod = c("1991-09-01", "2015-12-30"), pctile = 10)
res <- detect_event(ts, coldSpells = TRUE)
MCS <- res$climatology
MCS_g1sst_SB <- event_line(res, spread = 500, metric = "intensity_cumulative",
           start_date = "2011-12-31", end_date = "2014-10-30") +
  ggtitle("G1SST_SB")

combined_G1SST <- ggarrange(MCS_g1sst_PN, MCS_g1sst_LB, MCS_g1sst_O, MCS_g1sst_SP, MCS_g1sst_Kom, MCS_g1sst_YZ, MCS_g1sst_SB, ncol = 2, nrow = 4)
```

@@

ts <- ts2clm(OISST_PN, climatologyPeriod = c("1981-09-01", "2018-06-30"), pctile = 10)
res <- detect_event(ts, coldSpells = TRUE)
MCS <- res$climatology
MCS_OISST_PN <- event_line(res, spread = 900, metric = "intensity_cumulative",
           start_date = "2010-12-31", end_date = "2014-12-31") +
  ggtitle("OISST_PN")

@@

ts <- ts2clm(OISST_LB, climatologyPeriod = c("1981-09-01", "2018-06-30"), pctile = 10)
res <- detect_event(ts, coldSpells = TRUE)
MCS <- res$climatology
MCS_OISST_LB <- event_line(res, spread = 900, metric = "intensity_cumulative",
           start_date = "2010-12-31", end_date = "2014-12-31") +
  ggtitle("OISST_LB")

@@

ts <- ts2clm(OISST_SB, climatologyPeriod = c("1981-09-01", "2018-06-30"), pctile = 10)
res <- detect_event(ts, coldSpells = TRUE)
MCS <- res$climatology
MCS_OISST_SB <- event_line(res, spread = 500, metric = "intensity_cumulative",
           start_date = "2010-12-31", end_date = "2014-12-31") +
  ggtitle("OISST_SB")

@@

ts <- ts2clm(OISST_YZ, climatologyPeriod = c("1981-09-01", "2018-06-30"), pctile = 10)
res <- detect_event(ts, coldSpells = TRUE)
MCS <- res$climatology
MCS_OISST_YZ <- event_line(res, spread = 500, metric = "intensity_cumulative",
           start_date = "2010-12-31", end_date = "2014-12-31") +
  ggtitle("OISST_YZ")

@@

ts <- ts2clm(OISST_SP, climatologyPeriod = c("1981-09-01", "2018-06-30"), pctile = 10)
res <- detect_event(ts, coldSpells = TRUE)
MCS <- res$climatology
MCS_OISST_SP <- event_line(res, spread = 500, metric = "intensity_cumulative",
           start_date = "2010-12-31", end_date = "2014-12-31") +
  ggtitle("OISST_SP")

@@

ts <- ts2clm(OISST_Kom, climatologyPeriod = c("1981-09-01", "2018-06-30"), pctile = 10)
res <- detect_event(ts, coldSpells = TRUE)
MCS <- res$climatology
MCS_OISST_Kom <- event_line(res, spread = 500, metric = "intensity_cumulative",
           start_date = "2010-12-31", end_date = "2014-12-31") +
  ggtitle("OISST_Kom")

@@

ts <- ts2clm(OISST_O, climatologyPeriod = c("1981-09-01", "2018-06-30"), pctile = 10)
res <- detect_event(ts, coldSpells = TRUE)
MCS <- res$climatology
MCS_OISST_O <- event_line(res, spread = 900, metric = "intensity_cumulative",
           start_date = "2011-12-31", end_date = "2014-12-31") +
  ggtitle("OISST_O")

combined_OISST <- ggarrange(MCS_OISST_PN, MCS_OISST_LB, MCS_OISST_SB, MCS_OISST_YZ, MCS_OISST_O, MCS_OISST_Kom,MCS_OISST_SP, ncol = 2, nrow = 4)
```

# K10
Time series is less than 10 years and so the detection of MCS is not effective. 
heatwaveR package may be applied to datasets that have a climatological period of >10years
